Supplementary Information

### 2015-09-04 manuscript/supplement.tex
Un-commented the by-TL analyses

% \subsection*{Appendix S4: Scaling relationships by trophic level}

%   \subsubsection*{Methods}

%     We were also interested [[AE wants us to say why, because curiosity isn't a good reason to do science]] 
%     in the ways that scaling relationships with species richness might
%     be affected by changes to the distribution of species among trophic levels. To
%     that end, we repeated our analyses replacing species richness with the
%     proportion of basal resources, proportion of intermediate consumers,
%     or proportion of top predators. All model fitting procedures were identical to those
%     described for species richness. The model simplicication procedure was similar to
%     the procedure described for species richness, except that in some cases there were
%     multiple models with $\delta$AIC\textless2 that shared the minimal degrees of freedom.
%     In these cases, we defined the best-fitting model as the model with the lowest AIC in the
%     set of models with $\delta$AIC\textless2 and the minimal degrees of freedom.

%   \subsubsection*{Results}

%     The relationships between latitude and the proportions of species at each
%     trophic level were more complex than the flat relationship between latitude
%     and species richness in this dataset.  The proportion of basal resources
%     increased towards the poles in stream webs
%     ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
%     with latitude in estuarine, marine, lake, or terrestrial  food webs
%     ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
%     intermediate consumers decreased towards the poles in all ecosystem types
%     except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
%     $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
%     in a food web,  meanwhile, decreased towards the poles in lake and  stream
%     food webs but did not vary in other ecosystem types
%     ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
%     $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).

%     Unlike species richness, only generality showed an overall increase with
%     increasing proportions of basal resources in a web ($\beta_0$=0.019,
%     $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
%     link density, generality, and vulnerability, respectively;
%     Fig.~\ref{props_v_lat}). In each case, however, there were substantial
%     effects of latitude on the scaling relationships. Thus, the scaling
%     exponents for link density and vulnerability were negative for estuarine,
%     lake, and stream communities and became more negative towards the poles
%     ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
%     $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
%     density and vulnerability in marine and terrestrial communities, the overall
%     effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
%     $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
%     $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
%     $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
%     that there was weak scaling at most latitudes. In contrast, the scaling
%     exponent of generality with the proportion of basal resources was positive
%     near the equator and negative near the poles in estuarine, lake, and stream
%     communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
%     very little change in the scaling exponents for marine and terrestrial
%     communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
%     $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).

%     As with species richness, link density, generality, and vulnerability
%     generally increased with the proportion of intermediate consumers in a web
%     ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
%     $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
%     The best-fit models for link density and vulnerability did not include
%     any effect of latitude. In contrast, the strength of the scaling relationship
%     for generality increased weakly towards the poles in estuarine, marine, and
%     terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
%     towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
%     and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).

%     In contrast to the generally positive scaling relationships above, link
%     density, generality, and vulnerability decreased as the proportion of top
%     predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
%     $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
%     Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
%     strength of this scaling did not vary significantly with latitude
%     ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
%     $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
%     In stream and terrestrial food webs, however, scaling was more strongly negative in the 
%     tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
%     and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
%     $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
%     for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
%     for latitude in any ecosystem type.

@@

\subsection*{Appendix S5: supplemental figure}

@@

% \begin{figure}[h]
% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
% types and over latitude. For each property we show the estimated scaling exponent for species richness (black
% line) with its 95\% confidence interval (in grey),
% based on N=196 empirical food webs. Latitude is 
% given in degrees from the equator
% regardless of direction.}
% \label{S}
% \end{figure}

% \begin{figure}[!h]
% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
% types and over latitude. For each property we show the scaling exponent for the proportion of
% basal resources (black line) with its 95\% confidence interval (in grey), based on N=196 
% empirical food webs. Latitude is given in degrees
% from the equator regardless of direction.}
% \label{B}
% \end{figure}

% \newpage

% \begin{figure}[h]
% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
% types and over latitude. For each property we show the scaling exponent for the proportion of
% intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
% N=196 empirical food webs. Latitude is given in degrees
% from the equator regardless of direction.}
% \label{I}
% \end{figure}

% \begin{figure}[!h]
% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
% types and over latitude. For each property we show the scaling exponent for the proportion of
% top predators (black line) with its 95\% confidence interval (in grey), based on N=196 
% empirical food webs. Latitude is given in degrees
% from the equator regardless of direction.}
% \label{T}
% \end{figure}

>>>>

\subsection*{Appendix S4: Scaling relationships by trophic level}

    [[Explain why we were interested]]
    We were also interested [[AE wants us to say why, because curiosity isn't a good reason to do science]] 
    in the ways that scaling relationships with species richness might
    be affected by changes to the distribution of species among trophic levels. To
    that end, we repeated our analyses replacing species richness with the
    proportion of basal resources, proportion of intermediate consumers,
    or proportion of top predators. All model fitting procedures were identical to those
    described for species richness. The model simplicication procedure was similar to
    the procedure described for species richness, except that in some cases there were
    multiple models with $\delta$AIC\textless2 that shared the minimal degrees of freedom.
    In these cases, we defined the best-fitting model as the model with the lowest AIC in the
    set of models with $\delta$AIC\textless2 and the minimal degrees of freedom.

    The relationships between latitude and the proportions of species at each
    trophic level were more complex than the flat relationship between latitude
    and species richness in this dataset.  The proportion of basal resources
    increased towards the poles in stream webs
    ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
    with latitude in estuarine, marine, lake, or terrestrial  food webs
    ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
    intermediate consumers decreased towards the poles in all ecosystem types
    except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
    $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
    in a food web,  meanwhile, decreased towards the poles in lake and  stream
    food webs but did not vary in other ecosystem types
    ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
    $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).

    Unlike species richness, only generality showed an overall increase with
    increasing proportions of basal resources in a web ($\beta_0$=0.019,
    $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
    link density, generality, and vulnerability, respectively;
    Fig.~\ref{props_v_lat}). In each case, however, there were substantial
    effects of latitude on the scaling relationships. Thus, the scaling
    exponents for link density and vulnerability were negative for estuarine,
    lake, and stream communities and became more negative towards the poles
    ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
    $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
    density and vulnerability in marine and terrestrial communities, the overall
    effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
    $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
    $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
    $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
    that there was weak scaling at most latitudes. In contrast, the scaling
    exponent of generality with the proportion of basal resources was positive
    near the equator and negative near the poles in estuarine, lake, and stream
    communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
    very little change in the scaling exponents for marine and terrestrial
    communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
    $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).

    As with species richness, link density, generality, and vulnerability
    generally increased with the proportion of intermediate consumers in a web
    ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
    $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
    The best-fit models for link density and vulnerability did not include
    any effect of latitude. In contrast, the strength of the scaling relationship
    for generality increased weakly towards the poles in estuarine, marine, and
    terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
    towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
    and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).

    In contrast to the generally positive scaling relationships above, link
    density, generality, and vulnerability decreased as the proportion of top
    predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
    $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
    Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
    strength of this scaling did not vary significantly with latitude
    ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
    $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
    In stream and terrestrial food webs, however, scaling was more strongly negative in the 
    tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
    and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
    $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
    for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
    for latitude in any ecosystem type.

@@

\subsection*{Appendix S5: supplemental figures}

@@

\begin{figure}[!h]
\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts.eps}}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by species richness raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
see Fig.~\ref{TL_observed}.}
\label{TL_rescaled}
\end{figure}

\begin{figure}[!h]
\centerline{\includegraphics*[height=.75\textheight]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts_observed.eps}}
\caption{Scaling relationships for link density, generality, 
and vulnerability relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
For each relationship, we show observed values (white circles) and 
a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
any effects of habitat type or latitude (black line, N=196 food webs). See Fig.~\ref{TL_rescaled} to compare with 
observed values correcting for the effects of habitat type and latitude. }
\label{TL_observed}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey),
based on N=196 empirical food webs. Latitude is 
given in degrees from the equator
regardless of direction.}
\label{S}
\end{figure}

\begin{figure}[!h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
basal resources (black line) with its 95\% confidence interval (in grey), based on N=196 
empirical food webs. Latitude is given in degrees
from the equator regardless of direction.}
\label{B}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
N=196 empirical food webs. Latitude is given in degrees
from the equator regardless of direction.}
\label{I}
\end{figure}

\begin{figure}[!h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
top predators (black line) with its 95\% confidence interval (in grey), based on N=196 
empirical food webs. Latitude is given in degrees
from the equator regardless of direction.}
\label{T}
\end{figure}
